Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-11-11 numerical-amr.tex
Correcting a typo in the Jeans refinement criterion.
Correcting another error associated with the Jeans refinement criterion.  The equation doesn't include a factor of mu or gamma which are in the code.
Modified shear refinement criteria to reflect what is currently in code.

\begin{equation}
\Delta x < \left( \frac{\pi k_B T}{N_J^2 G \rho \mh} \right)^{1/2},
\end{equation}
where $J_J$ is the required number of cells per Jeans length (4 by default).

@@

\begin{equation}
\sum_i \sum_j \left( \frac{\partial v_i}{\partial x_j} \right)^2 -  \sum_i \left( \frac{\partial v_i}{\partial x_i} \right)^2
> \epsilon_s \frac{c_s^2}{\Delta x^2},
\end{equation}
where $\epsilon_s$ is a dimensionless parameter.

>>>>

\begin{equation}
\Delta x < \left( \frac{\gamma \pi k_B T}{N_J^2 G \rho \mu \mh} \right)^{1/2},
\end{equation}
where $N_J$ is the required number of cells per Jeans length (4 by default).

@@

\begin{equation}
\sum_i \sum_j \left( \frac{\partial v_i}{\partial x_j} \right)^2 -  \sum_i \left( \frac{\partial v_i}{\partial x_i} \right)^2
> \epsilon_s \frac{c_s^2}{\Delta x^2},
\end{equation}
where $\epsilon_s$ is a dimensionless parameter. The current
implementation assumes that $c_s$ is a constant and that $\Delta x$ in
the above expression is evaluated with the cell size on the level
being tested.
